---
title: "Merging legends from multiple geom object"
author: "Gilbert M."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
css: "sstyle.css"
#css: "bootstrap/css/bootstrap.css"
#javascript: "bootstrap/js/bootstrap.js"
---
I have result to write this article to save you hours or days trying to fix a simple but legitime issue.
The Problem,
I have estimates from list of regressions(for each years) including, the coeficient, the lower and upper interval limites. I want to plot the lines to see the trend, while adding a shade to the lines show their CI.
I expect the legend to show up as two lines as followed
but note two problem,
First we have

The coef(Incidence and Intensity) trends are plot with geom_line while the confidence interval are ploted with geom_ribon. Also there is an horitonal line to mark y=1.

Here is the inital code and what and its outpout

```{r, echo=FALSE, results="hide",include = FALSE }
# initial items that doesn't show
source(file = file.path("init.r"))
#sgdta <- reg1[avars=="staSchool372",.(year,coef,typ,lower,upper)]
#saveRDS(sgdta, file =file.path(rpath,"/share/data/sgdta.rds"))
sgdta <- readRDS(file =file.path(rpath,"/share/data/sgdta.rds"))



```
 
Here is my initial code and its output. 

```{r, echo=TRUE}
ggplot(sgdta,mapping =  aes(y = coef, x = year,ymin = lower,ymax = upper,group = typ, color = typ))+
  geom_line(aes(y=1,colour = "Reference"),linetype = "dashed",size = 0.1)+
  geom_line()+
  mygthemep+theme(
    strip.text = element_text(size = 7),
    axis.text.x = element_text(size = 7),
    aspect.ratio = 1/1.5)+
  geom_ribbon(aes(ymin=lower,ymax=upper,fill="99% Interval"),
              alpha=0.3, colour = NA)+
  scale_fill_manual(name="",values="#808080")+
  scale_colour_manual(name="",values=mygcolor[c(2,1,3)])+
  scale_y_continuous(name="ratio",breaks=seq(0,2,by=0.5), limits = c(0,2),
                     sec.axis = dup_axis())+
  scale_x_continuous(breaks=seq(1981,2017,by=9),sec.axis = dup_axis())

```

Althouhg it looks nice, I wanted to: Differenciate the lines type so that they can still be distinquisheble on black and white print.

for this to happen we need to 
add lty = typ
scale_linetype_manual(name="",values=c("dashed","solid","solid"))
replace geom_line(y=1,...) with
geom_line(aes(y=1,color = "Reference",lty = "Reference"),size = 0.1)+
guides(color = guide_legend(override.aes = list(fill = "white")))+

```{r, echo=TRUE}
ggplot(sgdta,mapping =  aes(y = coef, x = year,ymin = lower,ymax = upper,
                              group = typ, color = typ,lty = typ))+
  geom_line(aes(y=1,color = "Reference",lty = "Reference"),size = 0.1)+
  geom_line()+
  mygthemep+theme(
    strip.text = element_text(size = 7),
    axis.text.x = element_text(size = 7),
    aspect.ratio = 1/1.5)+
  geom_ribbon(aes(ymin=lower,ymax=upper,fill="99% Interval"),
              alpha=0.3, colour = NA)+
  scale_fill_manual(name="",values="#808080")+
  scale_linetype_manual(name="",values=c("dashed","dotted","solid"))+
  guides(color = guide_legend(override.aes = list(fill = "white")))+
  scale_colour_manual(name="",values=mygcolor[c(2,1,3)])+
  scale_y_continuous(name="ratio",breaks=seq(0,2,by=0.5), limits = c(0,2),
                     sec.axis = dup_axis())+
  scale_x_continuous(breaks=seq(1981,2017,by=9),sec.axis = dup_axis())

```
